%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------

\documentclass[a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[margin = 0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{amsmath}

%--------------UNDERLINING---------------
% taken from https://alexwlchan.net/2017/10/latex-underlines/

\usepackage{contour}
\usepackage{ulem}

\renewcommand{\ULdepth}{3.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

%----------------------------------------

%\graphicspath{ {./Images/} }

%----------FONT OPTIONS----------
\usepackage{fontspec}
\usepackage{fontawesome5}
\setmainfont[ExternalLocation=Fonts/]{Junicode.ttf}%
  [Ligatures=TeX,
  BoldFont=Junicode-Bold.ttf,
  ItalicFont=Junicode-Italic.ttf,
  BoldItalicFont=Junicode-BoldItalic.ttf]

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\iffalse
% \iftrue
\addtolength{\oddsidemargin}{0.3in}
\addtolength{\marginparsep}{0.3in}
\addtolength{\evensidemargin}{0.3in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{0.3in}
\addtolength{\textheight}{0.3in}
\fi

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    {\color{gray}\titlerule} \vspace{-5pt}
    \vspace{8pt}\scshape\raggedright\large
}{}{0pt}{}

%-------------------------
% Custom commands
\newcommand{\BlueHref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

\newcommand{\resumeItem}[1]{
  \item\large{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & \normalsize #2 \\
      \textit{\large #3} & \textit{\normalsize #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\large#1} & \textit{\large #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------

{\Huge Niks Skersts}
\\
$|$
\BlueHref{https://www.linkedin.com/in/niks-skersts/}{
    \faLinkedin
    \thinspace \thinspace        
    \myuline{niks-skersts}} $|$
\BlueHref{https://github.com/NiksSkersts}{
    \faGithub
    \thinspace \thinspace
    \myuline{NiksSkersts}} $|$
\BlueHref{mailto:cv@nikssk.id.lv}{
    \faEnvelope
    \thinspace \thinspace
    \myuline{cv@nikssk.id.lv}} $|$

%-----------EDUCATION-----------
% Samainīt vietām vietu un datumu, lai būtu vienots formāts visā CV
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Latvia University of Life Sciences and Technologies}{2019 -- 2023}
      {Bachelor Degree of Engineering in Computer Control and Computer Science}{Jelgava, Latvia}
    \resumeItemListStart
     \resumeItem{
     Bachelor Thesis: "IPv6 ieviešana Latvijas Biozinātņu un tehnoloģiju universitātē".\\ 
     ENG: Deployment of IPv6 protocol at Latvia University of Life Sciences and Technologies.
     }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {IT Manager}{June 2024 -- Present }
      {SIA TBMarine Shipmanagement (Riga)}{Riga, Latvia}
      \resumeItemListStart
        \resumeItem{Maintenance of Ansible, Zabbix, Docker, and and various Docker software containers.}
        \resumeItem{Responsible for disaster recovery system setup, maintenance, and monitoring.}
        \resumeItem{Upkeep of Linux server and Windows environment.}
        \resumeItem{Windows and Linux support for end-users at shore and at sea.}
      \resumeItemListEnd

      \resumeSubheading
      {Service Engineer}{October 2021 -- June 2024  }
      {Latvia University of Life Sciences and Technologies}{Jelgava, Latvia}
      \resumeItemListStart
        \resumeItem{Duties include upkeep of Windows workstations, GNU/Linux servers, software, and its licensing, printers, copiers, and work with OSI L1, L2 networking.}
        \resumeItem{End-user support in Windows environment.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
      
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \large{\item{
     \textbf{Languages}{: Latvian - native, English - B2.}\\
     \textbf{Basic knowledge at}{:}
     \resumeItemListStart
        \resumeItem{C\#, Python, PLSQL, HTML/CSS, BASH, and Powershell. I am not much of a programmer, but I can write a script to get the job done.}
        \resumeItem{Various tools like Putty, Tabby.sh, Wireshark, NMAP, Clonezilla, and IPerf. List is always growing as time goes. Tools come and go.}
     \resumeItemListEnd
     \textbf{Good knowledge at}{:}
     \resumeItemListStart
        \resumeItem{Administering and troubleshooting Windows OS and GNU/Linux OS (mainly Debian and Debian based systems like Proxmox).}
        \resumeItem{Ansible for automating system upkeep and configuration. Recently moved from CLI to using \BlueHref{https://semaphoreui.com/}{\myuline{SemaphoreUI}} as frontend. }
        \resumeItem{Docker container deployment and upkeep. A lot of is now being done using Ansible.}
        \resumeItem{Deployment and upkeep of physical infrastructure - servers and networking. }
     \resumeItemListEnd
     \textbf{Great knowledge at}{: This section is left intentionally blank. Working at SMBs comes with an disadvantage of being jack of all trades, master of none. \newline However, I can use Google, so that's great. }\\
     \textbf{Lack of knowledge at}{: Windows AD (I am dealing with device, user, app management on Intunes, but lack knowledge on more advanced topics). }
     }}
 \end{itemize}
 
\section{Interests \& Goals}
\large{Major Thanks goes to the folk from whom I am able to learn and keep myself updated:}
\resumeItemListStart
\resumeItem{\textbf{Podcasts:} \BlueHref{https://latenightlinux.com/}{Late Night Linux Family}, \BlueHref{https://blog.apnic.net/ping-podcast/}{PING by APNIC}, \BlueHref{https://labs.ripe.net/category/podcasts/}{The RIPE Labs Podcast by RIPE}, \BlueHref{https://enterpriselinuxsecurity.show/}{Enterprise Linux Security}, \BlueHref{https://packetpushers.net/}{Packet Pushers}}
\resumeItem{\textbf{General:} \BlueHref{https://www.jeffgeerling.com/}{Jeff Geerling} for Ansible, \BlueHref{https://klarasystems.com/}{Klara Systems} mainly for dealing with ZFS and server administration. }
\resumeItem{\textbf{Fun:} \BlueHref{https://tuxdigital.com/}{TuxDigital Network}, \BlueHref{https://www.jupiterbroadcasting.com/}{Jupiter Broadcasting}, \BlueHref{https://twit.tv/}{TWiT}}
\resumeItemListEnd
\begin{flushright}
    \small{(This CV is open source at \BlueHref{https://github.com/NiksSkersts/CV}{Github}).}
\end{flushright}


%-------------------------------------------
\end{document}
